The Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-02-08 ms.tex
moreabstract

\begin{abstract}
We calculate steady-state, one-dimensional hydrodynamic profiles of hot gas in the nuclei of quiescent galaxies for a range of black hole masses $M_{\bullet}$, parameterized gas heating rates, and physically-motivated stellar density profiles.  Mass is supplied to the circumnuclear medium (CNM) by stellar winds, while gas is heated by a combination of stellar winds, supernovae, and black hole feedback.  Analytic estimates are derived for quantities including the stagnation radius (where the radial velocity of the gas passes through zero) and the black hole accretion rate as a function of $M_{\bullet}$ and heating efficiency, the latter of which is related to the star-formation history of the stellar population.  We assess over under conditions radiative instability will develop, based on the average star formation history for galaxies with a given black hole mass.  Our results for the average accretion rates, as well as the maximum thermally-stable and -unstable accreion rates, are compared to the measured nuclear X-ray luminosities of a sample of quiescent black holes, from which we conclude that...  We briefly discuss implications of our results for the use of an assumed $\dot{M}-M_{\bullet}$ relationship to constrain the occupation fraction of SMBHs in low mass galaxies and the diversity of CNM environments encountered by the jetted outflows from tidal disruption events.
\end{abstract}

>>>>

\begin{abstract}
We calculate steady-state, one-dimensional hydrodynamic profiles of hot gas in the nuclei of quiescent galaxies for a range of black hole masses $M_{\bullet}$, parameterized gas heating rates, and physically-motivated stellar density profiles.  Mass is supplied to the circumnuclear medium (CNM) by stellar winds, while gas is heated by a combination of stellar winds, supernovae, and black hole feedback.  Analytic estimates are derived for quantities including the stagnation radius (where the radial velocity of the gas passes through zero) and the black hole accretion rate, $\dot{M}$, as a function of $M_{\bullet}$ and heating efficiency, the latter of which is related to the star-formation history of the stellar population.  We assess over under conditions radiative instability will develop, based on the average star formation history for galaxies corresponding to a given black hole mass.  Results for the average accretion rate, as well as the maximum thermally-stable and -unstable accretion rates, are compared to the nuclear X-ray luminosities of a sample of quiescent black holes.  We find that the high accretion rates and short growth times of low mass black holes in the low redshift universe must be the result of an external gas supply, rather than secular processes from stellar mass loss within the galactic nucleus.  We briefly discuss implications of our results for the use of an assumed $\dot{M}-M_{\bullet}$ relationship to constrain the occupation fraction of SMBHs in low mass galaxies and the diversity of CNM environments encountered by the jetted outflows from tidal disruption events.
\end{abstract}
